\setlinespacing{1.1}

\chapter{Introduction and Background} \label{sec:introduction}

\section{The Game}

The game is a puzzle adventure. It uses programming logic to solve the puzzles presented. 

\subsection{Serious Games}


\section{Architectural Patterns}
Describes how the MVC relates to my project

\subsection{MVC}

Using MVC architectural patterns are a common choice for games development. It is favoured for its modular
 approach. The separation of the model view controller interfaces allow me to build on each module without disturbing the other. When i need to expand on the development of the model class, i will be able to do with ease. There will be minimal, if any, disturbance's to the rest of the program. When the changes are made from the model class, those changes can be displayed to the user interface.

The LevelModel class represents the structure of data that holds the attributes of a level design. The LevelView class will display the attributes to the user interface . The LevelController class is used to exchange data between the two objects. In the case of this project, the LevelController will also manage the Input controller. 


	
\subsubsection{Model}

\subsubsection{View}

\subsubsection{Controller}



\subsection{Singleton}

\subsubsection{Don't Destroy On Load}



\section{Test Driven Development}

\subsection{Subsection header 1}

\newpage

\newpage

\section{Git Hub, Version Control}

\section{Games Development}

\subsection{Unity Engine}

level editor

reading file

NetHack ...

\begin{description}
	
 \item[C\#, Syntax, Refactoring:]
 
\end{description}






